---
title: "my first presentation"
author: "Yan Li"
date: "17 January 2017"
output: ioslides_presentation
---



## My new slide

```{r,echo=FALSE,background='Blue',fig.align='center',fig.cap='My awsome figure'}
plot(mtcars$wt,mtcars$mpg,xlab="Weight",ylab="MPG")
```

Plain text

*italicized text*

**Bold text**

'for (i %in% 1 : 10)'

## My title
- Bullet 1
- Bullet 2

1. Item a
2. Item b

### A top level subheading
#### A second level subheading



## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

